---
title: "Castor EDC, R format factor variables"
#subtitle: ""
author: "Erik Erhardt"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 5
    number_sections: false
    code_folding: show
  pdf_document:
    toc: yes
    toc_depth: 5
    number_sections: false
---

<!---
## IGNORE THIS
#   Bummer, automatic date doesn't work for Knit PDF:  date: "`r format(Sys.time(), '%B %d, %Y')`"
# Erik's compile commands in R:
  rm(list=ls())
  #dev.off(dev.list()["RStudioGD"])  # close all plots
  fn.this <- "Castor_CRF_export_R_FormatVariables.Rmd"
  setwd("C:/Dropbox/StatAcumen/consult/Industry/2018_CastorEDC_FormatR/CastorR/vignettes")
  library(knitr)
  knitr::purl(fn.this)
  rmarkdown::render(fn.this)
#
# In case you're curious about what the code above does:
# The purl()   command strips out all the code chunks and writes them to an *.R file
# The render() command does the same as the "Knit HTML" button,
#   but all the variables are created in the console.
# I use these commands because I use a different text editor than RStudio.
## IGNORE THIS
-->

```{R, echo=FALSE}
knitr::opts_chunk$set(comment = NA, message = FALSE, warning = FALSE, width = 100)
knitr::opts_chunk$set(fig.align = "center", fig.height = 4, fig.width = 6)
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(cache = TRUE, autodep=TRUE)  #$
knitr::opts_chunk$set(cache = FALSE) #, autodep=TRUE)  #$
```

# Installing from source

Set the appropriate path and run this command:
```{r, eval=FALSE}
install.packages("./Analysis/Code/CastorR_0.1.00.tar.gz", repos = NULL, type="source")
```

# Strategy for labeling factor variables

1. Read data
    * Read all `CRF_export.xlsx` file sheets and construct the structures to produce an Rdata file with (1) variable question labels, (2) correct factor levels with labels, and (3) correct data and numeric data types.
    * Data in `Study results` has labels in `Study variable list`
    * Data in other data sheets (between `Study results` and `Study variable list`) has labels in `Report variable list`
    * All factor groups with labels and levels are in `Field options`
2. Collect Option group names, levels, and labels
    * `Field options` gives the factor variable levels and labels
    * `Option group name`
    * `Option name` labels list with `Option value` list
3. Assign variable question labels, Factor variables with Option groups, assign varible class data types
    * `Study variable list` gives the question names for `Study results`
    * `Report variable list` gives the question names for other data sheets (between `Study results` and `Study variable list`)
    * `Variable name`
    * `Field label` is the question name
    1. Use `library(labelled)` with `var_label()`
    2. For each variable, label it.
    * `Optiongroup name`
    1. Use `factor()` for each variable using `Option group name` labels and levels
    * `Field type` variable data class, useful for date, datetime, and numeric.


# Format Castor CRF data

```{r}
library(CastorR)
dat <- castor_format_R(fn = "CRF_export_2.xlsx")
str(dat)
```




```{r, eval=FALSE, echo=FALSE}
## Print codebook generated by the data
ggplot2::theme_set(ggplot2::theme_bw())
pander::panderOptions("table.split.table", Inf)
library(codebook)
codebook(dat$`Study results`)
```

